Applied Measure Theory for Probabilistic Modeling

### 2022-05-13 paper/paper.tex
edits

Finally, kernels are key to expressing \href{https://en.wikipedia.org/wiki/Likelihood_function}{\emph{likelihoods}}, which we can use to formulate Bayesian conjugacy properties. We'll discuss this further in Section~\ref{Likelihoods}.

@@

Let us momentarily assume the common case of Lebesgue base measure. For a parameter $\theta$ and data $x$, suppose we have a \href{https://en.wikipedia.org/wiki/Prior_probability}{\emph{prior density}} $p(\theta)$ and \href{https://en.wikipedia.org/wiki/Likelihood_function}{\emph{likelihood}} $p(x | \theta)$. Then Bayes's Law gives the posterior density
\[
p(\theta \mid x) = \frac{p(\theta)\ p(x \mid \theta)}{p(x)}\ .
\]

In practice, we rarely know the normalization factor $p(x)$, so we often work in terms of the unnormalized posterior density, and write
\[
{\underbrace{p(θ \mid x)}_\text{posterior}}
 \propto 
{\underbrace{p(\theta)}_\text{prior}}\ 
{\underbrace{p(x \mid \theta)}_\text{likelihood}} .
\]
Because the product does not include normalization, in general it does not integrate to one, and so it's not a probability density function. But there are no such problems as a density for a measure.

>>>>

@@

To begin, let's consider the case of probability distributions dominated by Lebesgue measure.
For a parameter $\theta$ and data $x$, suppose we have a \href{https://en.wikipedia.org/wiki/Prior_probability}{\emph{prior density}} $p(\theta)$ and \href{https://en.wikipedia.org/wiki/Likelihood_function}{\emph{likelihood}} $p(x | \theta)$. Then Bayes's Law gives the posterior density
\[
p(\theta \mid x) = \frac{p(\theta)\ p(x \mid \theta)}{p(x)}\ .
\]

In practice, we rarely know the normalization factor $p(x)$, so we often work in terms of the unnormalized posterior density, and write
\[
{\underbrace{p(θ \mid x)}_\text{posterior}}
 \propto 
{\underbrace{p(\theta)}_\text{prior}}\ 
{\underbrace{p(x \mid \theta)}_\text{likelihood}} .
\]
Because the product does not include normalization, in general it does not integrate to one, and so it's not a probability density function. But there are no such problems as a density for a measure. We now consider this more general formulation.
